Rotations and Insecticide Resistance initial plots

### 2017-11-21 inst/documents/rotations_notes.Rmd
fixing few glitches, tidying
tidy insecticide switching

@@

>>>>

Ians text removed from the insecticide switching portion of code

  #NOTE. At the moment if all but one of the insecticides are over the threshold frequency, the one under the threshold
  #will be repeatedly deployed. For example, if there are 3 insecticides and rotation is every 10 generations. 
  #if #3 is being deployed and due to rotate out at generetion 100: if only #3 is under the threshold
  #it will not rotate out, but will continue to be used util the next scheduled rotation at which point
    #(a) it will continue to be use if it is the only one below the threshold 
    #(b) it will be replaced if one of the other insecticides is now below the threshold due to fitness effects or migration
    #(c) the simulation will terminate if all insecticides exceed the threshold

@@

~ take the insecticide switching out into its own function(s)

~ create a new version of run_rot2() allowing me to refactor the code and check that it still generates same results as run_rot()
